MSD panels 1, 2 and 3 Explant Supernatant

### 2016-10-03 MSD_panels_1_2_3_explant_sup_analysis.Rmd
added a new heatmap just showing a few analytes

>>>>

This is a heat map showing the same data as above, but fewer analytes
```{r analyte subset heatmap, echo=FALSE}

#want a heat map that just shows CXCL9, IL-1a, IL-10 and MIP-1b, in that order.

#I'm making a vector of the ones I want so I can avoid typing the stupid greek letters.

assaysIwant<- levels(merge24And3$altAssayNames)
assaysIwant<- assaysIwant[c(6,9,17,20)]

analyteSubset<- merge24And3 %>%
  filter(altAssayNames %in% assaysIwant)

#Recall that the order of the factors well get plotted bottom to top, to the one you want at the BOTTOM of hte axis needs to be in factor positiojn [1]
analyteSubset$altAssayNames <- factor(analyteSubset$altAssayNames, levels (analyteSubset$altAssayNames) [c(6,9,17,20)])

ggplot(analyteSubset, aes(x = Donor, y = altAssayNames))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0, name = "log10 Fold Change")+
  facet_wrap(~Virus, scales = "free_x")+
  labs( y = "Assay")+
  scale_y_discrete(breaks = merge24And3$altAssayNames,labels =merge24And3$altAssayNames)+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")
